Spatial Reasoning and Statistical Graphics

### 2014-10-20 Paper/Draft1/TestingVisualAptitude.Rnw
New lineup demographic characteristics appendix w/ model data.

>>>>

\subsection{Lineup Performance and Demographic Characteristics}\label{app:categoricalresults}

<<ttests.categ, echo=F, results='asis'>>=
tmp <- dlply(lineup.summary.categorical, .(variable), function(df){
    tmp <- anova(lm(lineup~factor(value, ordered=F), data=df))
    coefs <- as.data.frame(tmp)[1,]
    coefs$level <- gsub("factor(value, ordered = F)", unique(df$variable), rownames(coefs), fixed=T)
    rownames(coefs) <- NULL
    coefs <- coefs[,c(6, 1:5)]
    names(coefs) <- c("Variable", "DF", "Sum.of.Squares", "Mean.Squared", "F.value", "p.value")
    coefs
})

tmp <- rbind.fill(tmp)
tmp <- tmp[order(tmp$p.value, decreasing=F),]
print(xtable(tmp, digits=c(1, 1, 0, 3, 3, 2, 3), caption="Model results of each demographic variable compared with lineup score. Multiple testing issues aside, it appears that very few demographic variables (if any) are significantly associated with score on lineups among Iowa State undergraduate students."), include.rownames=F)
@
